### 2021-02-14 rad-icfp-2021/background.tex
some comments

\section{Pure $\lambda$-calculus for differentiable programming} % (fold)
\label{sec:pure_lambda_calculus_for_differentiable_programming}

@@

>>>>

\section{Pure $\lambda$-calculus for differentiable programming} 
\label{sec:pure_lambda_calculus_for_differentiable_programming}

@@

\MH{is this useful to present both languages? not sure. also not sure when to talk about the restrictions for efficiency. but again it's a theory paper mostly so we don't want to talk too much about that. just a ref to some papers that do that too.}
\MH{will probably just be a subsection}
